Supplementary Materials for \\ Modeling the competing effects of the immune system and EMT on epithelial cancers

### 2019-12-02 Paper/Supplement/CleanSupplement.tex
finished this round of edits!

@@

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/SinglePatientBlue.jpg}}
\caption{
Single patient trajectory without immune cells targeting premalignant cells.
}
\label{fig:1b_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/OneSurvivalCurve.jpg}}
\caption{
Sample cohort survival curve without immune cells targeting premalignant cells.
}
\label{fig:1c_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure2/Figure2.jpg}}
\caption{
Morris-OAT global sensitivity without immune cells targeting premalignant cells.
}
\label{fig:2_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure3/Figure3_first.pdf}}
\caption{
Effects of mesenchymal tumor cell properties on the Time to Cancer without immune cells targeting premalignant cells.
}
\label{fig:3_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure4/Figure4_first.pdf}}
\caption{
Effects of inflammation on the Time to Cancer without immune cells targeting premalignant cells.
}
\label{fig:4_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure5/MIEvsMGA_bigcbar.jpg}}
\caption{
Summary of the contrasting effects of MIE and MGA on Time to Cancer without immune cells targeting premalignant cells.
}
\label{fig:5_first}
\end{figure}

>>>>

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/SKCM.pdf}}
\caption{A. K-means clustering of SKCM using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of SKCM using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of SKCM using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:SKCM}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LUAD.pdf}}
\caption{A. K-means clustering of LUAD using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LUAD using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LUAD using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LUAD}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/SinglePatientBlue.jpg}}
\caption{
Single patient trajectory without immune cells targeting premalignant cells. Compare to Fig. 1B.
}
\label{fig:1b_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/OneSurvivalCurve.jpg}}
\caption{
Sample cohort survival curve without immune cells targeting premalignant cells. Compare to Fig. 1C.
}
\label{fig:1c_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure2/Figure2.jpg}}
\caption{
Morris-OAT global sensitivity without immune cells targeting premalignant cells. Compare to Fig. 2.
}
\label{fig:2_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure3/Figure3_first.pdf}}
\caption{
Effects of mesenchymal tumor cell properties on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 3.
}
\label{fig:3_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure4/Figure4_first.pdf}}
\caption{
Effects of inflammation on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 4.
}
\label{fig:4_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure5/MIEvsMGA_bigcbar.jpg}}
\caption{
Summary of the contrasting effects of MIE and MGA on Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 5.
}
\label{fig:5_first}
\end{figure}
